---
output:
  word_document: default
  html_document: default
---
# BAN 502 Week 3 Assignment

## Josh Cooper 

```{r}
library(tidyverse)
library(tidymodels)
library(e1071) 
library(ROCR) 
library(glmnet)
```

```{r}
parole <- read_csv("parole.csv")
parole = parole %>% mutate(male = as_factor(male))%>%
  mutate(male = fct_recode(male, "male" = "1", "female" = "0" ))
parole = parole %>% mutate(race = as_factor(race)) %>%
  mutate(race = fct_recode(race, "white" = "1", "other" = "2" )) 
parole = parole %>% mutate(state = as_factor(state)) %>%
  mutate(state = fct_recode(state, "other" = "1", "kentucky" = "2", "Louisana"= "3", "Virginia"="4" ))
parole = parole %>% mutate(multiple.offenses = as_factor(multiple.offenses)) %>%
  mutate(multiple.offenses = fct_recode(multiple.offenses, "multiple" = "1", "other" = "0" )) 
parole = parole %>% mutate(violator = as_factor(violator)) %>%
  mutate(violator = fct_recode(violator, "violation" = "1", "no violation" = "0" ))
parole = parole %>%
  mutate(crime = as_factor(crime)) %>%
  mutate(crime = fct_recode(crime, "1" = "Other", "2" = "Larceny", "3" = "Drug", "4" = "Driving"))
   
```

```{r}
set.seed(12345)
parole_split = initial_split(parole, prop = .70, strata = violator)
train = training(parole_split)
test = testing(parole_split)
```

```{r}
ggplot(train, aes(x=crime, fill=violator)) +
  geom_bar() +
  theme_bw()
ggplot(train, aes(x=multiple.offenses, fill=violator)) +
  geom_bar() +
  theme_bw()
ggplot(train, aes(x=max.sentence, fill=violator)) +
  geom_bar() +
  theme_bw()
ggplot(train, aes(x=race, fill=violator)) +
  geom_bar() +
  theme_bw()
```

Using the chart it shows that the crime 1 has the more violators of their parole. Crime 1 is any crime other than crime 2 larceny, crime 3 drug-related and crime 4 driving-related.

Using multiple offenses we can see that people on parole with multiple offenses are more likely to violate their parole.

While Race and max sentence show if they are correlated and they seem to be 

I wanted to see both to see which one looks like they have a stronger correlation to commit a violation

```{r}
parole_model = 
  logistic_reg() %>%
  set_engine("glm") 

parole_recipe = recipe(violator ~ multiple.offenses, parole) %>%
  step_dummy(all_nominal(), -all_outcomes())  

logreg_wf = workflow() %>%
  add_recipe(parole_recipe) %>% 
  add_model(parole_model)

parole_fit = fit(logreg_wf, parole)
```

```{r}
summary(parole_fit$fit$fit$fit)
```

The model shows a strong correlation between those who are multiple offenders and if that violated their parole.

```{r}
train_model = 
  logistic_reg() %>%
  set_engine("glm") 

train_recipe = recipe(violator ~ multiple.offenses + max.sentence, train) %>%
  step_dummy(all_nominal(), -all_outcomes())  

logreg_wf = workflow() %>%
  add_recipe(train_recipe) %>% 
  add_model(train_model)

train_fit = fit(logreg_wf, train)
```

```{r}
summary(train_fit$fit$fit$fit)
```

Using max sentence and multiple offenses as the factors into violators both were significant in seeing if they are correlated.

```{r}
train_model2 = 
  logistic_reg() %>%
  set_engine("glm") 

train_recipe2 = recipe(violator ~ multiple.offenses + state + race, train) %>%
  step_dummy(all_nominal(), -all_outcomes())  

logreg_wf = workflow() %>%
  add_recipe(train_recipe2) %>% 
  add_model(train_model)

train_fit2 = fit(logreg_wf, train)
```

```{r}
summary(train_fit2$fit$fit$fit)
```
The state of kentucky and the other in the race category are not significant and compared to the other model it is not as strong as it.

```{r}
Parolee1 = data.frame(state="Louisana", multiple.offenses="multiple", race="white")
predict(train_fit2, Parolee1, type="prob")
```

```{r}
Parolee2 = data.frame(state="kentucky", multiple.offenses="other", race="other")
predict(train_fit2, Parolee2, type="prob")
```

```{r}
train_model = 
  logistic_reg(mode = "classification") %>% 
  set_engine("glm") 

train_recipe3 = recipe(violator ~., train)

logreg_wf = workflow() %>%
  add_recipe(train_recipe3) %>% 
  add_model(train_model)

train_fit3 = fit(logreg_wf, train)
```

```{r}
prediction = predict(train_fit3, train, type="prob") 
```

```{r}
predictions = predict(train_fit3, train, type="prob") [2] 
```


```{r}
ROCRpred = prediction(predictions, train$violator) 
ROCRperf = performance(ROCRpred, "tpr", "fpr")
plot(ROCRperf, colorize=TRUE, print.cutoffs.at=seq(0,1,by=0.1), text.adj=c(-0.2,1.7))
```

As we move down the curve from 0 to .7, showing that at .8 and a threshold of .1 that those people will be violators of their parole at a true positive rate of .8.

```{r}
as.numeric(performance(ROCRpred, "auc")@y.values)
```
Making that around 86% of the box will be filled in.

```{r}
opt.cut = function(perf, pred){
    cut.ind = mapply(FUN=function(x, y, p){
        d = (x - 0)^2 + (y-1)^2
        ind = which(d == min(d))
        c(sensitivity = y[[ind]], specificity = 1-x[[ind]], 
            cutoff = p[[ind]])
    }, perf@x.values, perf@y.values, pred@cutoffs)
}
print(opt.cut(ROCRperf, ROCRpred))
```

```{r}
t1 = table(train$violator,predictions >  0.1193651)
t1
```

```{r}
(t1[1,1]+t1[2,2])/nrow(train)
```
Miss classifying a parolee can be very bad and that it could get them back in jail. 

```{r}
t1 = table(train$violator,predictions > 0.45)
t1
(t1[1,1]+t1[2,2])/nrow(train)
```

```{r}
t1 = table(train$violator,predictions > 1)
t1
(t1[1])/nrow(train)
```

```{r}
t1 = table(train$violator,predictions > .45)
t1
```

Using the .45 we were able to get a better prediction on the estimates of people who would violate their parole